\enablemode[papercolor,euler,wide]
\environment /home/adityam/Projects/presentations/slides-v3
\setupbodyfont[slidefont,14.4pt]

\starttext

\setvariables
  [metadata]
  [
    title={ECSE 506: Stochastic Control and Decision Theory},
    author={Aditya Mahajan},
    date={6 Jan 2022},
  ]



\startslide[title={Learning objectives}]
  \startitemize
    \item Develop ability to read and understand research papers in stochastic
      control.

    \item Emphasis on understanding proofs. We will prove \bold{every} result
      that we state in class.

    \item Study examples from different application domains: communications,
      operations research, control systems, and power systems. Focus on being able
      to establish qualitative properties of optimal policies

    \item Understand the role and limitations of models.

  \stopitemize
\stopslide

\startslide[title={Course content}]
  \startitemize
    \starthead {Stochastic optimization}
      \startindented
        Single decision made by single decision maker.
      \stopindented
    \stophead

    \starthead {MDPs (Markov decision processes}
      \startindented
        \emph{Multiple} decisions made by single DM with perfect information
      \stopindented
    \stophead

    \starthead {POMDPs (Partially observable MDPs}
      \startindented
        Multiple decisions made by a single DM with \emph{imperfect}
        information.
      \stopindented
    \stophead

    \starthead {Decentralized control (also called Dec-POMDPs}
      \startindented
        Multiple decisions made by \emph{multiple} DMs with imperfect info.
      \stopindented
    \stophead
  \stopitemize
\stopslide

\startslide[title={Background}]
\startitemize
  \starthead {Graduate probability}
    \startindented
      Conceptual understanding of random variables and conditional
      expectation
    \stopindented
  \stophead

  \starthead {Real analysis}
    \startindented
      Basic understanding of limits and convergence, metric spaces, and
      completeness.
    \stopindented
  \stophead

  \starthead {Optimization}
    \startindented
      Basic understanding of convexity and first and second order conditions
      for optimality.
    \stopindented
  \stophead
\stopitemize
\stopslide

\startslide[title={Logistics}]
  \startitemize
      \starthead {Assignments (20\%)}
        \startitemize[itemize:nested,fit][distance=0.5em]
          \item \emph{Weekly} assignments; posted on the course website. 
          \item Only one randomly selected question will be graded. Lowest
            assignment dropped.
          \item Solutions posted on myCourses and only accessible to
            registered students. 
          \item If you are auditing and need access, send me a message.
        \stopitemize
      \stophead

    \starthead {Mid Term (40\%)}
      \startitemize[itemize:nested,fit][distance=0.5em]
        \item \important{If classes are online: Week of 28th March}
          \crlf
          Online exam. Available for 72hrs. Once you start, you'll have 2.5hrs
          to finish the exam.

        \item \important{If classes are in-person: 29th March}
          \crlf
          In person, 1.5 hr exam, during class time.

      \stopitemize
    \stophead

    \starthead {Term Project (20\%)}
      \startitemize[itemize:nested,fit][distance=0.5em]
        \item To be done either alone or in groups of two. Due end of term
        \item Critique one or two papers related to the course.
         Deliverables: project report and presentation.
      \stopitemize
    \stophead
  \stopitemize
\stopslide

\startslide[title={Course Notes}]
\startitemize
  \item Partial course notes available on the course website:
    \crlf
    {\tt{https://adityam.github.io/stochastic-control}}

  \item While classes are online, the zoom recording will be available on
    myCourses.

  \item If/when in-person classes resume, video recordings may not be
    available.\crlf
    (Most rooms don't have video recording infrastructure).
\stopitemize
\stopslide

\startslide[title={Communication}]

  \startitemize
    \item Announcements and solutions posted on myCourses. Please check
      regularly.

    \item All communication with the instruction should be via the discussion
      board on myCoures.
  \stopitemize

\stoptext
